SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-05-04 scipy-1.0/paper.tex
Tightened Benchmark suite section Removed the command to generate the figure. As #117 records, it doesn't "just work", so I don't think it's worth including. Removed the material after the figure about how to use asv. To me it seemed like a short tutorial on how to use asv with SciPy, which seemed out of place. Removed the last part of "allows us to objectively measure that our code base is improving~~, to empower scientific applications.~~" Reworded "generally remains constant or improves over the commit hash history of the project" -> "improves over time." Reworded "the performance of the Sc

The Airspeed Velocity (\texttt{asv}\cite{asvref}) library enables benchmarking Python packages
over their lifetimes, and the performance of the SciPy code base was monitored
with \texttt{asv} starting in February of 2015 (PR \#4501). In addition to ensuring that
unit tests are passing, confirming 
that performance generally
remains constant or improves over the commit hash history of the project allows
us to objectively measure that our code base is improving, to empower
scientific applications.

Consider the (\texttt{asv} benchmark results shown in Figure~\ref{fig:asvbench}, spanning
roughly nine years of project history. These demonstrate the gradual
performance improvements in a nearest-neighbor search through
\texttt{scipy.spatial.cKDTree.query()}, and can be run using:

\texttt{python run.py run -e -s 800 --bench "\textbackslash
btime\_query\textbackslash b" "02de46a546..b3ddb2c"},

where \texttt{run.py} is a light wrapper script around \texttt{asv}
that is packaged with SciPy.

@@

Any pull request can be compared against the \texttt{master} branch with the
command \texttt{asv continuous master new-feature}. This will provide a
benchmark against the \texttt{master} branch and the branch a new feature is implemented
in. More features are available in the \texttt{asv} documentation\cite{asvdocs}, including 
arguments to select which benchmarks to run.

>>>>

In addition to ensuring that unit tests are passing, it is important to confirm that the
the performance of the SciPy codebase improves over time. Since February 2015, the
performance of SciPy has been monitored with Airspeed Velocity (\texttt{asv} \cite{asvref}).
SciPy's \texttt{run.py} script conveniently wraps \texttt{asv} features such that benchmark 
results over time can be generated with a single console command. For example,
Figure~\ref{fig:asvbench} illustrates the improvement of\texttt{scipy.spatial.cKDTree.query}
over roughly nine years of project history.

@@
